---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# schwartzGeohashPM 

<!-- badges: start -->
[![R build status](https://github.com/degauss-org/schwartzGeohashPM/workflows/R-CMD-check/badge.svg)](https://github.com/degauss-org/schwartzGeohashPM/actions)
<!-- badges: end -->

The goal of schwartzGeohashPM is to add PM2.5, NO2, and O3 concentrations to your data based on geohashed locations (usually output from the [Schwartz Grid Lookup Container](https://github.com/degauss-org/schwartz_grid_lookup))

## Installation 

You can install addSchwartzGeohashPM from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("degauss-org/schwartzGeohashPM")
```

## s3 downloads

This package utilizes the [s3 package](https://github.com/geomarker-io/s3). Users can pass arguments for `s3::s3_get_files` to  `schwartzGeohashPM::add_schwartz_pollutants`. This is especially useful for specifying the local path where s3 files will be downloaded onto the user's local machine, via the `download_folder` argument. The download folder can also be specified by setting options.

```
options(s3.download_folder = /path/to/folder/s3_downloads)
```


## Example

```{r, echo = F}
reticulate::use_condaenv("r-s3", required = TRUE)
```


```{r example, warning = F}
library(schwartzGeohashPM)

d <- tibble::tribble(
      ~id,         ~lat,    ~lon, ~site_index,      ~sitecode,  ~start_date,    ~end_date,
      '55000100280', 39.2, -84.6,   '9607238', 211050640897, '2008-09-09', '2008-09-11',
      '55000100281', 39.2, -84.6,   '9607238', 211050640897, '2007-08-05', '2007-08-08',
      '55000100282', 39.2, -84.6,   '9607238', 211050640897, '2015-08-31', '2015-09-02') %>%
    dplyr::mutate_at(dplyr::vars(start_date, end_date), as.Date)

add_schwartz_pollutants(d)
```

